Tweets

### 2020-05-10 Rmd/tweets.Rmd
updated tweets analysis code

```{r}
rtweet::stream_tweets(
  timeout = (60 * 5),
  parse = TRUE,
  file_name = paste0("../data/", lubridate::now(), "-tweets")
)
```

@@

```{r}
library(magrittr)
```

```{r}
tweets <- rtweet::parse_stream("../data/2020-04-09 16:31:44-tweets.json") %>%
  dplyr::filter(lang == "en") %>%
  tidytext::unnest_tokens(output = word, input = text)
```

@@

>>>>

```{r}
rtweet::stream_tweets(
  timeout = (15),
  parse = FALSE,
  file_name = paste0("../data/", lubridate::now(), "-tweets")
)
```

@@

```{r}
library(magrittr)
source("https://gist.githubusercontent.com/JBGruber/dee4c44e7d38d537426f57ba1e4f84ab/raw/ab87bebb8d020c2f96c71a40a483dc96a4c80e54/recover_stream.R")
```

```{r}
tweets <- recover_stream(path = "../data/2020-05-10 10:36:09-tweets.json", verbose = TRUE) %>%
  dplyr::filter(lang == "en") %>%
  tidytext::unnest_tokens(output = word, input = text)
```

@@

```{r}
tweets_dtm <- word_counts %>%
  tidytext::cast_dtm(status_id, word, n)
```

```{r}
tweets_lda <- topicmodels::LDA(tweets_dtm, k = 8)
```

```{r}
tweets_beta <- tidytext::tidy(tweets_lda, matrix = "beta")
```

```{r}
tweets_top_terms <- tweets_beta %>%
  dplyr::group_by(topic) %>%
  dplyr::top_n(10, beta) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(topic, -beta)
```

```{r}
tweets_top_terms %>%
  dplyr::mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot2::ggplot(ggplot2::aes(term, beta, fill = factor(topic))) +
  ggplot2::geom_col(show.legend = FALSE) +
  ggplot2::facet_wrap(~ topic, scales = "free") +
  ggplot2::coord_flip()
```

```{r}
tweets_gamma <- tidytext::tidy(tweets_lda, matrix = "gamma")
tweets_gamma
```

```{r, eval = FALSE}
# too many documents to plot all
tweets_gamma %>%
  dplyr::mutate(title = reorder(document, gamma * topic)) %>%
  ggplot2::ggplot(ggplot2::aes(factor(topic), gamma)) +
  ggplot2::geom_boxplot() +
  ggplot2::facet_wrap(~ document)
```
